Bioconductor workflow for single-cell RNA sequencing: Normalization, dimensionality reduction, clustering, and lineage inference

### 2017-06-29 workflow/workflow.Rmd
Updates to text.

```{r stemcelldiff, echo=FALSE, out.width='60%', fig.align='center', fig.cap = 'Stem cell differentiation in the mouse olfactory epithelium. This figure was reproduced with kind permission from (Fletcher et al. 2017).'}
knitr::include_graphics('stemcelldiff_Fletcher2017_2e.png')
```

@@

Throughout the workflow, we use an object of class `SummarizedExperiment` to keep track of the counts and their associated metadata within a single object. The cell-level metadata contain quality control (QC) measures, sequencing batch ID, and cluster and lineage labels from the original publication [@Fletcher2017]. Cells with a cluster label of `-2` were not assigned to a cluster in the original publication.

@@

```{r scone, fig.cap="Plot generated by scone to filter low quality cells.", eval=FALSE}
# QC-metric-based sample-filtering
data("housekeeping")
hk = rownames(se)[toupper(rownames(se)) %in% housekeeping$V1]

@@

```{r zinbschema, echo=FALSE, out.width='95%', fig.cap="Schematic view of the ZINB-WaVE model. This figure was reproduced with kind permission from (Risso et al. 2017)."}
knitr::include_graphics('zinb_schema.pdf')
```

@@

```{r curves, fig.cap="Cells colored by cluster in a 4-dimensional space with smooth curves representing each inferred lineage."}
pairs(lineages, type='curves', pal[primaryClusterNamed(ceObj)])
```

```{r tree, fig.cap="Cells colored by cluster in a 4-dimensional space with connecting lines between cluster centers representing the inferred structure."}
pairs(lineages, type='lineages', col = pal[primaryClusterNamed(ceObj)])
```

>>>>

```{r stemcelldiff, echo=FALSE, out.width='60%', fig.align='center', fig.cap = 'Stem cell differentiation in the mouse olfactory epithelium. This figure was reproduced with kind permission from Fletcher et al. (2017).'}
knitr::include_graphics('stemcelldiff_Fletcher2017_2e.png')
```

@@

Throughout the workflow, we use an object of class `SummarizedExperiment` to keep track of the counts and their associated metadata within a single object. The cell-level metadata contain quality control measures, sequencing batch ID, and cluster and lineage labels from the original publication [@Fletcher2017]. Cells with a cluster label of `-2` were not assigned to a cluster in the original publication.

@@

```{r scone, fig.cap="Plot generated by scone to filter low-quality cells.", eval=FALSE}
# QC-metric-based sample-filtering
data("housekeeping")
hk = rownames(se)[toupper(rownames(se)) %in% housekeeping$V1]

@@

```{r zinbschema, echo=FALSE, out.width='95%', fig.cap="Schematic view of the ZINB-WaVE model. This figure was reproduced with kind permission from Risso et al. (2017)."}
knitr::include_graphics('zinb_schema.pdf')
```

@@

```{r curves, fig.cap="Cells color-coded by cluster in a 4-dimensional space with smooth curves representing each inferred lineage."}
pairs(lineages, type='curves', pal[primaryClusterNamed(ceObj)])
```

```{r tree, fig.cap="Cells color-coded by cluster in a 4-dimensional space with connecting lines between cluster centers representing the inferred structure."}
pairs(lineages, type='lineages', col = pal[primaryClusterNamed(ceObj)])
```
